Illusion Game Validation (Study 2)

### 2022-08-27 study2/study2.Rmd
update

cache <- TRUE
runModels <- TRUE
bestModels <- TRUE
fig.width <- see::golden_ratio(7)
fig.height <- 7

@@

# Fix
df[df$Illusion_Type == "Rod-Frame" & df$Date == "05/08/2022", "Illusion_Strength"] <- -1 * (df[df$Illusion_Type == "Rod-Frame" & df$Date == "05/08/2022", "Illusion_Strength"])

@@

df <- read.csv("../data/study2.csv") |>
  mutate(
    Date = lubridate::dmy(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    Illusion_Side = as.factor(Illusion_Side),
    # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
    Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
    Block = as.factor(Block),
    Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
  )

@@

outliers <- c(
  # Error rate of 48.8% Very short RT
  # Prolific Status: REJECTED (06/08)
  "5e66ed53de7896486f9a71f8_p8ckk",
  # 2nd block of responses very fast
  # Prolific Status: REJECTED (15/08)
  "61443e47c248a375c899a0cf_9qz3u"
)

partial_outliers <- c(
  # 2nd block a bit bad
  "5c43cd414fe4f800016e4983_0zp37", 
  # Entire 2nd block bad
  "61564e378e974bdbe42763a2_hhufm")
```

@@

```{r message=FALSE, warning=FALSE, fig.width=20, fig.height=20}
# RT distribution
p <- df |> 
  # filter(Date > "2022-08-12") |> 
  filter(RT < 10000) |> 
  estimate_density(select = "RT", at = c("Participant", "Block")) |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  mutate(Participant = factor(Participant, levels=levels(df$Participant))) |> 
  mutate(color = ifelse(Participant %in% outliers, "red", ifelse(Participant %in% partial_outliers, "orange", "blue"))) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(filter(df, RT < 10000), select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = color, group = interaction(Participant, Block), linetype = Block)) +
  geom_vline(xintercept = 125, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("red" = "#F44336", "orange" = "#FF9800", "blue" = "blue"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  coord_cartesian(xlim = c(0, 3000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~Participant) +
  labs(y = "", x = "Reaction Time (ms)")
# p
# ggsave("figures/outliers.png", p, width=20, height=15)

@@

p1 <- estimate_density(df, select = "RT", at = "Participant") |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  merge(df |>
    filter(Error == 0) |>
    group_by(Participant) |>
    summarize(Outlier = mean(RT) + 4 * sd(RT))) |>
  mutate(Outlier = ifelse(x >= Outlier, TRUE, FALSE)) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(filter(df, RT < 10000), select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = Participant, linetype = Outlier), alpha=0.2) +
  geom_vline(xintercept = c(125), linetype = "dashed", color = "red") +
  scale_color_material_d("rainbow", guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  guides(linetype = "none") +
  coord_cartesian(xlim = c(0, 4000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  labs(y = "", x = "Reaction Time (ms)")

@@

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  select(Participant, Age, Sex, Education, Nationality, Ethnicity, Duration, Break_Duration, Screen_Resolution, Screen_Refresh, Device_OS, starts_with("IPIP6"), starts_with("PID5")) |>
  slice(1) |>
  ungroup()
```

@@

p6 <- plot_waffle(dfsub, "Nationality") +
  scale_fill_manual(values = c("South American" = "#FF5722", "Middle Eastern" = "#FF9800", "Western" = "#2196F3", "African" = "#4CAF50", "South African" = "#009688"))

@@

@@

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  Error ~ sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect +
    (1 + sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect | Participant),
  family = "bernoulli"
)

@@

save(model_delboeuf_err, file="models/model_delboeuf_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_delboeuf_err.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_delboeuf_err <- plot_model_err(data, model_delboeuf_err)
p_delboeuf_err
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~ sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect +
    (1 + sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect | Participant),
  sigma ~ 1 + (1 | Participant),
  beta ~ 1 + (1 | Participant),
  family = "exgaussian"
)

# brms::get_prior(formula, data = data)
# plot(seq(-5, 5, length.out=100), brms::dstudent_t(seq(-5, 5, length.out=100), df = 3, 0.1, 0.5))
priors <- c(
  # Intercept
  prior("student_t(3, 0, 0.1)", class = "Intercept"),
  prior("student_t(3, 0.35, 0.1)", class = "sd", coef="Intercept", group="Participant"),
  # Default parameters
  prior("student_t(3, 0, 3)", class = "b"),
  prior("student_t(3, 0.35, 0.5)", class = "sd", group="Participant")

@@

plot_ppcheck(model_delboeuf_rt)
# performance::check_model(model_delboeuf_rt)
# parameters::parameters(model)

save(model_delboeuf_rt, file="models/model_delboeuf_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_delboeuf_rt.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_delboeuf_rt <- plot_model_rt(data, model_delboeuf_rt)
p_delboeuf_rt
```

@@

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  Error ~ sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect +
    (1 + sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect | Participant),
  family = "bernoulli"
)

@@

save(model_ebbinghaus_err, file="models/model_ebbinghaus_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_ebbinghaus_err.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_ebbinghaus_err <- plot_model_err(data, model_ebbinghaus_err)
p_ebbinghaus_err
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~ sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect +
    (1 + sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect | Participant),
  sigma ~ 1 + (1 | Participant),
  beta ~ 1 + (1 | Participant),
  family = "exgaussian"
)

@@

plot_ppcheck(model_ebbinghaus_rt)
# performance::check_model(model_delboeuf_rt)
# parameters::parameters(model)

save(model_ebbinghaus_rt, file="models/model_ebbinghaus_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_ebbinghaus_rt.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_ebbinghaus_rt <- plot_model_rt(data, model_ebbinghaus_rt)
p_ebbinghaus_rt
```

@@

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  Error ~ sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect +
    (1 + sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect | Participant),
  family = "bernoulli"
)

@@

save(model_rodframe_err, file="models/model_rodframe_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_rodframe_err.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_rodframe_err <- plot_model_err(data, model_rodframe_err)
p_rodframe_err
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~ sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect +
    (1 | Participant),
  sigma ~ 1 + (1 | Participant),
  beta ~ 1 + (1 | Participant),
  family = "exgaussian"
)

@@

plot_ppcheck(model_rodframe_rt)
# performance::check_model(model_delboeuf_rt)
# parameters::parameters(model)

save(model_rodframe_rt, file="models/model_rodframe_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_rodframe_rt.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_rodframe_rt <- plot_model_rt(data, model_rodframe_rt)
p_rodframe_rt
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  Error ~ sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect +
    (1 | Participant),
  family = "bernoulli"
)

@@

save(model_verticalhorizontal_err, file="models/model_verticalhorizontal_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_verticalhorizontal_err.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_verticalhorizontal_err <- plot_model_err(data, model_verticalhorizontal_err)
p_verticalhorizontal_err
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~ sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect +
    (1 | Participant),
  # sigma ~ t2(Illusion_Difference * Illusion_Strength) +
  #   (1 | Participant),
  family = "exgaussian"
)

model_verticalhorizontal_rt <- brms::brm(formula,
  data = data,
  refresh = 0
)

plot_ppcheck(model_verticalhorizontal_rt)
# performance::check_model(model_verticalhorizontal_rt)
# parameters::parameters(model)

save(model_verticalhorizontal_rt, file="models/model_verticalhorizontal_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_verticalhorizontal_rt.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_verticalhorizontal_rt <- plot_model_rt(data, model_verticalhorizontal_rt)
p_verticalhorizontal_rt
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  Error ~ logmod(Illusion_Difference) * abs(Illusion_Strength) * Illusion_Effect +
    (1 | Participant),
  family = "bernoulli"
)

@@

save(model_zollner_err, file="models/model_zollner_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_zollner_err.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_zollner_err <- plot_model_err(data, model_zollner_err)
p_zollner_err
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~ logmod(Illusion_Difference) * abs(Illusion_Strength) * Illusion_Effect +
    (1 | Participant),
  # sigma ~ t2(Illusion_Difference * Illusion_Strength) +
  #   (1 | Participant),
  family = "exgaussian"
)

model_zollner_rt <- brms::brm(formula,
  data = data,
  refresh = 0
)

@@

save(model_zollner_rt, file="models/model_zollner_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_zollner_rt.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_zollner_rt <- plot_model_rt(data, model_zollner_rt)
p_zollner_rt
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  Error ~ sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect +
    (1 + sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect | Participant),
  family = "bernoulli"
)

@@

model_white_err <- brms::brm(formula,
  data = data,
  refresh = 0
)

@@

model_mullerlyer_err <- brms::brm(formula,
  data = data,
  refresh = 0
)

@@

### Reliability

>>>>

cache <- TRUE
runModels <- FALSE
bestModels <- FALSE
fig.width <- see::golden_ratio(7)
fig.height <- 7

@@

# Fix due to technical issue in the paradigm on the first day
df[df$Illusion_Type == "Rod-Frame" & df$Date == "05/08/2022", "Illusion_Strength"] <- -1 * (df[df$Illusion_Type == "Rod-Frame" & df$Date == "05/08/2022", "Illusion_Strength"])
df[df$Illusion_Type == "Rod-Frame" & df$Date == "05/08/2022", "Illusion_Effect"] <- ifelse(sign(df[df$Illusion_Type == "Rod-Frame" & df$Date == "05/08/2022", "Illusion_Strength"]) == -1, "Congruent", "Incongruent")

@@

df <- read.csv("../data/study2.csv") |>
  mutate(
    Date = lubridate::dmy(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    Illusion_Side = as.factor(Illusion_Side),
    # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
    Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
    Block = as.factor(Block),
    Education = fct_relevel(Education, "High School", "Bachelor", "Master", "Doctorate", "Other", "Prefer not to Say")
  )

@@

dfsub$Participant[grepl("60be8d", dfsub$Participant)]

outliers <- c(
  # Error rate of 48.8% Very short RT
  # Prolific Status: REJECTED (06/08)
  "5e66ed53de7896486f9a71f8_p8ckk",
  # 2nd block of responses very fast
  # Prolific Status: REJECTED (15/08)
  "61443e47c248a375c899a0cf_9qz3u",
  # Error rate of 44% and very short RTs
  # Prolific Status: RETURN REQUESTED (22/08)
  "60dd626e212aa26c16d953b7_vw35k",
  # 2nd block bad, first block 1/3 bad
  # Prolific Status: RETURN REQUESTED (26/08)
  "5eed37c13661d91555c38308_hpgnt",
  # Prolific Status: RETURN REQUESTED (26/08)
  "6159f8a9a2d80ecf1a5acd30_zc8rt",
  # Prolific status: accepted (not enough proof)
  "6136aa846e80ebd7daf6e148_aggf6"
)

partial_outliers <- c(
  # 2nd block a bit bad
  "5c43cd414fe4f800016e4983_0zp37", 
  # Entire 2nd block bad
  "61564e378e974bdbe42763a2_hhufm",
  # Entire 2nd block bad
  "5ff8b21dd2ca6f12bdaa5be8_c5rs6",
  # Half of 2nd block bad
  "613a9193ed68e49209b471b7_wrymn",
  # 2nd block not good
  "60be8dd61cec210d627483de_cmfx4")
```

@@

```{r message=FALSE, warning=FALSE, fig.width=20, fig.height=20}
# RT distribution
p <- df |> 
  # filter(Date > "2022-08-24") |>
  filter(RT < 10000) |> 
  estimate_density(select = "RT", at = c("Participant", "Block")) |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |> 
  mutate(color = ifelse(Participant %in% outliers, "red", ifelse(Participant %in% partial_outliers, "orange", "blue"))) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(filter(df, RT < 10000), select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = color, group = interaction(Participant, Block), linetype = Block)) +
  geom_vline(xintercept = 125, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("red" = "#F44336", "orange" = "#FF9800", "blue" = "blue"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  coord_cartesian(xlim = c(0, 3000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~Participant) +
  labs(y = "", x = "Reaction Time (ms)")
# p
# ggsave("figures/outliers.png", p, width=25, height=25)

@@

p1 <- df |> 
  filter(RT < 10000) |> 
  estimate_density(select = "RT", at = "Participant") |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  merge(df |>
    filter(Error == 0) |>
    group_by(Participant) |>
    summarize(Outlier = mean(RT) + 4 * sd(RT))) |>
  mutate(Outlier = ifelse(x >= Outlier, TRUE, FALSE)) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(filter(df, RT < 10000), select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = Participant, linetype = Outlier), alpha=0.2) +
  geom_vline(xintercept = c(125), linetype = "dashed", color = "red") +
  scale_color_material_d("rainbow", guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  guides(linetype = "none") +
  coord_cartesian(xlim = c(0, 4000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  labs(y = "", x = "Reaction Time (ms)")

@@

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  select(Participant, Age, Sex, Ethnicity, Education, Nationality, Duration, Break_Duration, Device_OS, starts_with("Screen"), starts_with("IPIP6"), starts_with("PID5")) |>
  slice(1) |>
  ungroup()
```

@@

p6 <- plot_waffle(dfsub, "Nationality") +
  scale_fill_manual(values = c("South American" = "#FF5722", "Middle Eastern" = "#FF9800", "Western" = "#2196F3", "Eastern" = "#673AB7", "African" = "#4CAF50", "South African" = "#009688"))

@@

## Data Analysis

In the first part of the study focuses on modelling the effect of illusion strength and task difficulty, on errors and reaction time, within each illusion. In order to achieve that, we will start by fitting a General Additive Models (GAM), which can accommodate possible non-linear effects and interactions. Using them as a "ground-truth", we will attempt at approximating them using general linear models, in which we can specify a participant-level variability of the effects (via random effects).

We will then extract this participant-level variability in the effect of illusion strength, task difficulty and their interaction and use it as inter-individual features. We will estimate the relationship across different illusions using factor analysis (FA) and structural equation modelling (SEM).

```{r make_GAMs, message=FALSE, warning=FALSE, eval=runModels}
for(ill in c("Delboeuf", 
             "Ebbinghaus", 
             "Rod-Frame",
             "Vertical-Horizontal", 
             "Zöllner",
             "White",
             "Müller-Lyer", 
             "Ponzo", 
             "Poggendorff",
             "Contrast")) {
  print(ill)
  model <- brms::brm(
    Error ~ t2(Illusion_Difference, Illusion_Strength, k=8, bs="cr") + (1 | Participant),
    data = filter(df, Illusion_Type == ill),
    family = "bernoulli",
    algorithm="sampling"
  )

  name <- paste0("gam_", tolower(clean_illusionName(ill)), "_err")
  assign(name, model)  # Rename with string
  save(list=name, file=paste0("models/", name, ".Rdata"))

  model <- brms::brm(
    brms::bf(
      RT ~ t2(Illusion_Difference, Illusion_Strength, k=8, bs="cr") + (1 | Participant),
      sigma ~ t2(Illusion_Difference, Illusion_Strength, k=8, bs="cr") + (1 | Participant),
      beta ~ t2(Illusion_Difference, Illusion_Strength, k=8, bs="cr") + (1 | Participant)
    ),
    data = filter(df, Illusion_Type == ill, Error == 0),
    family = "exgaussian",
    init=0,
    algorithm="sampling"
  )

  name <- paste0("gam_", tolower(clean_illusionName(ill)), "_rt")
  assign(name, model)  # Rename with string
  save(list=name, file=paste0("models/", name, ".Rdata"))
}
```

# Results

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=bestModels}
best_models(data)

m1 <- glmmTMB::glmmTMB(Error ~ sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect + (1 | Participant), data = data, family = "binomial")
m2 <- glmmTMB::glmmTMB(Error ~ sqrt(Illusion_Difference) * sqrtmod(Illusion_Strength) + (1 | Participant), data = data, family = "binomial")

compare_performance(m1, m2, metrics = c("R2", "BIC"))
test_performance(m1, m2)
```

@@

```{r m_err_delboeuf, message=FALSE, warning=FALSE, eval=runModels}
formula <- brms::bf(
  Error ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) +
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) | Participant),
  family = "bernoulli"
)

@@

save(model_delboeuf_err, file="models/model_delboeuf_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_delboeuf_err.RData")
load("models/gam_delboeuf_err.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_delboeuf_err <- plot_model_err(data, model_delboeuf_err, gam_delboeuf_err)
p_delboeuf_err
```

@@

```{r m_rt_delboeuf, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)))  +
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) | Participant),
  sigma ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) + (1 | Participant),
  beta ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) + (1 | Participant),
  family = "exgaussian"
)

# brms::get_prior(formula, data = data)
# plot(seq(-5, 5, length.out=100), brms::dstudent_t(seq(-5, 5, length.out=100), df = 3, 0.1, 0.5))
priors <- c(
  # Intercept
  # prior("student_t(3, 0, 0.1)", class = "Intercept"),
  # prior("student_t(3, 0.35, 0.1)", class = "sd", coef="Intercept", group="Participant"),
  # Default parameters
  # prior("student_t(3, 0, 3)", class = "b"),
  # prior("student_t(3, 0.35, 0.5)", class = "sd", group="Participant")

@@

save(model_delboeuf_rt, file="models/model_delboeuf_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_delboeuf_rt.RData")
load("models/gam_delboeuf_rt.RData")

plot_ppcheck(model_delboeuf_rt)
# performance::check_model(model_delboeuf_rt)
# parameters::parameters(model)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_delboeuf_rt <- plot_model_rt(data, model_delboeuf_rt, gam_delboeuf_rt)
p_delboeuf_rt
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=bestModels}
best_models(data)

m1 <- glmmTMB::glmmTMB(Error ~ sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect +
    (1 | Participant), data = data, family = "binomial")
m2 <- glmmTMB::glmmTMB(Error ~ sqrt(Illusion_Difference) * logmod(Illusion_Strength) +
    (1 | Participant), data = data, family = "binomial")

test_performance(m1, m2)
compare_performance(m1, m2)
```

@@

```{r m_err_ebbinghaus, message=FALSE, warning=FALSE, eval=runModels}
formula <- brms::bf(
  Error ~ Illusion_Effect / (sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength))) +
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength))) | Participant),
  family = "bernoulli"
)

@@

save(model_ebbinghaus_err, file="models/model_ebbinghaus_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_ebbinghaus_err.RData")
load("models/gam_ebbinghaus_err.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_ebbinghaus_err <- plot_model_err(data, model_ebbinghaus_err, gam_ebbinghaus_err)
p_ebbinghaus_err
```

@@

```{r m_rt_ebbinghaus, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength)))  +
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength))) | Participant),
  sigma ~ Illusion_Effect / (sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength))) + (1 | Participant),
  beta ~ Illusion_Effect / (sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength))) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_ebbinghaus_rt, file="models/model_ebbinghaus_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_ebbinghaus_rt.RData")
load("models/gam_ebbinghaus_rt.RData")

plot_ppcheck(model_ebbinghaus_rt)
# performance::check_model(model_delboeuf_rt)
# parameters::parameters(model)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_ebbinghaus_rt <- plot_model_rt(data, model_ebbinghaus_rt, gam_ebbinghaus_rt)
p_ebbinghaus_rt
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=bestModels}
best_models(data)

m1 <- glmmTMB::glmmTMB(Error ~ logmod(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect +
    (1 | Participant), data = data, family = "binomial")
m2 <- glmmTMB::glmmTMB(Error ~ logmod(Illusion_Difference) * logmod(Illusion_Strength) +
    (1 | Participant), data = data, family = "binomial")

compare_performance(m1, m2)
test_performance(m1, m2)
```

@@

```{r m_err_rodframe, message=FALSE, warning=FALSE, eval=runModels}
formula <- brms::bf(
  Error ~ Illusion_Effect / (logmod(Illusion_Difference) * logmod(Illusion_Strength)) +
    (1 + Illusion_Effect / (logmod(Illusion_Difference) * logmod(Illusion_Strength)) | Participant),
  family = "bernoulli"
)

@@

save(model_rodframe_err, file="models/model_rodframe_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_rodframe_err.RData")
load("models/gam_rodframe_err.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_rodframe_err <- plot_model_err(data, model_rodframe_err, gam_rodframe_err)
p_rodframe_err
```

@@

```{r m_rt_rodframe, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) +
    (1 + Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) | Participant),
  sigma ~ Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) + (1 | Participant),
  beta ~ Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_rodframe_rt, file="models/model_rodframe_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_rodframe_rt.RData")
load("models/gam_rodframe_rt.RData")

plot_ppcheck(model_rodframe_rt)
# performance::check_model(model_delboeuf_rt)
# parameters::parameters(model)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_rodframe_rt <- plot_model_rt(data, model_rodframe_rt, gam_rodframe_rt)
p_rodframe_rt
```

@@

```{r m_err_verticalhorizontal, message=FALSE, warning=FALSE, eval=runModels}
formula <- brms::bf(
  Error ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) +
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) | Participant),
  family = "bernoulli"
)

@@

save(model_verticalhorizontal_err, file="models/model_verticalhorizontal_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_verticalhorizontal_err.RData")
load("models/gam_verticalhorizontal_err.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_verticalhorizontal_err <- plot_model_err(data, model_verticalhorizontal_err, gam_verticalhorizontal_err)
p_verticalhorizontal_err
```

@@

```{r m_rt_verticalhorizontal, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) +
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) | Participant),
  sigma ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) + (1 | Participant),
  beta ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) + (1 | Participant),
  family = "exgaussian"
)

model_verticalhorizontal_rt <- brms::brm(formula,
  data = data,
  refresh = 100,
  init = 0
)

save(model_verticalhorizontal_rt, file="models/model_verticalhorizontal_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_verticalhorizontal_rt.RData")
load("models/gam_verticalhorizontal_rt.RData")

plot_ppcheck(model_verticalhorizontal_rt)
# performance::check_model(model_verticalhorizontal_rt)
# parameters::parameters(model)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_verticalhorizontal_rt <- plot_model_rt(data, model_verticalhorizontal_rt, gam_verticalhorizontal_rt)
p_verticalhorizontal_rt
```

@@

```{r m_err_zollner, message=FALSE, warning=FALSE, eval=runModels}
formula <- brms::bf(
  Error ~ Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) +
    (1 + Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) | Participant),
  family = "bernoulli"
)

@@

save(model_zollner_err, file="models/model_zollner_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_zollner_err.RData")
load("models/gam_zollner_err.RData")
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_zollner_err <- plot_model_err(data, model_zollner_err, gam_zollner_err)
p_zollner_err
```

@@

```{r m_rt_zollner, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~  Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) +
    (1 + Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) | Participant),
  sigma ~  Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) +
    (1 | Participant),
  beta ~ Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) +
    (1 | Participant),
  family = "exgaussian"
)

model_zollner_rt <- brms::brm(formula,
  data = data,
  refresh = 100,
  init = 0
)

save(model_zollner_rt, file="models/model_zollner_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_zollner_rt.RData")
load("models/gam_zollner_rt.RData")

@@

```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_zollner_rt <- plot_model_rt(data, model_zollner_rt, gam_zollner_rt)
p_zollner_rt
```

@@

```{r m_err_white, essage=FALSE, warning=FALSE, eval=runModels}
formula <- brms::bf(
  Error ~ Illusion_Effect / (Illusion_Difference * sqrt(abs(Illusion_Strength))) +
    (1 + Illusion_Effect / (Illusion_Difference * sqrt(abs(Illusion_Strength))) | Participant),
  family = "bernoulli"
)

@@

model_white_err <- brms::brm(formula,
  data = data,
  refresh = 100
)

@@

model_mullerlyer_err <- brms::brm(formula,
  data = data,
  refresh = 100
)

@@

### Model-based Descriptors
